### 2011-06-21 standing-patches-paper.tex
/* The Next Paper */ intro notes

Reference on parallel adapation, standing variation, etc.:
  coop,
  pennings and hermisson,

@@

Stick to constant-speed waves.

@@

>>>>

References on parallel adapation, standing variation, etc.:
  coop,
  pennings and hermisson.
Note pennings and hermisson found standing deleterious variation was very important.

recall peromyscus examples with patchy environments

@@

@@

Stick to constant-speed waves.
Note monty's empircal speeds paper.
